
% From https://www.overleaf.com/learn/latex/Glossaries

\makeglossaries

\setabbreviationstyle[acronym]{long-postshort-user}
\glssetcategoryattribute{acronym}{nohyperfirst}{true}
\setabbreviationstyle{short-nolong}

% \renewcommand*{\glsxtruserparen}[2]{%
%     \glsxtrfullsep{#2}% space between long part and parenthetical material
%     (\glshyperlink[#1]{#2})%
% }

\newglossaryentry{asyncio}{name=\code{asyncio},description={A Python library for asynchronous code using coroutines, event loops, and tasks.}}
\newglossaryentry{dash}{name=Plotly Dash,description={A Python framework for building web applications for data visualization.}}
\newglossaryentry{debayer}{name=Debayer,description={A process to convert raw image data into a full-color image.}}
\newglossaryentry{deepstream}{name=DeepStream,description={A platform by NVIDIA for AI-powered video analytics applications.}}
\newglossaryentry{dgpu}{name=dGPU,description={Discrete Graphics Processing Unit for graphics-intensive tasks.}}

\newglossaryentry{f9p}{name=F9P,description={A high-precision, dual band GNSS receiver module.}}
\newglossaryentry{flask}{name=Flask,description={A lightweight Python web framework.}}
\newglossaryentry{gigev}{name=GigE Vision,description={An industrial camera interface standard for high-speed vision systems.}}
\newglossaryentry{gstreamer}{name=GStreamer,description={An open-source multimedia framework for video tasks.}}
\newglossaryentry{gviz}{name=Graphviz,description={A graph visualization software.}}
\newglossaryentry{h264}{name=H.264,description={A widely used video compression standard.}}
\newglossaryentry{h265}{name=H.265,description={A video compression standard with improved efficiency.}}
\newglossaryentry{ide}{name=IDE,description={Integrated Development Environment for software development.}}
\newglossaryentry{igpu}{name=iGPU,description={Integrated Graphics Processing Unit.}}
\newglossaryentry{jetlinux}{name=NVIDIA Jetson Linux,description={A Linux distribution for NVIDIA Jetson devices.}}
\newglossaryentry{jetpack}{name=JetPack,description={A software development package for the Jetson platform.}}
\newglossaryentry{jetsonclocks}{name=jetson\_clocks,description={A utility for adjusting Jetson device settings.}}
\newglossaryentry{jinja}{name=Jinja2,description={A popular templating engine for Python.}}
\newglossaryentry{jpeg}{name=JPEG,description={A commonly used image compression format.}}
\newglossaryentry{jtop}{name=jtop,description={A command-line tool for monitoring Jetson Nano devices.}}
\newglossaryentry{mp4}{name=MP4,description={A digital multimedia container format.}}
\newglossaryentry{nforum}{name=NVIDIA Developer Forum,description={An online community for NVIDIA developers.}}
\newglossaryentry{nvpmodel}{name=\code{nvpmodel},description={A command-line utility for setting Jetson power mode.}}
\newglossaryentry{pyds}{name=Python DeepStream,description={A Python library for DeepStream.}}
\newglossaryentry{pygo}{name=PyGobject,description={A Python package for GObject library.}}
\newglossaryentry{quart}{name=Quart,description={A Python web framework based on Flask and \code{asyncio}.}}
\newglossaryentry{stdin}{name=\code{stdin},description={Standard Input for program input.}}
\newglossaryentry{stdout}{name=\code{stdout},description={Standard Output for program output.}}
\newglossaryentry{swap}{name=SWAP,description={Secondary storage used as an extension of RAM.}}
\newglossaryentry{tegra}{name=Tegra,description={NVIDIA system-on-a-chip (SoC) processors.}}
\newglossaryentry{tmpfs}{name=\code{tmpfs},description={Temporary file system using RAM.}}
\newglossaryentry{vlc}{name=VLC media player,description={Open-source multimedia player.}}
\newglossaryentry{volta}{name=Volta GPU,description={NVIDIA GPU architecture.}}
\newglossaryentry{vscode}{name=Visual Studio Code,description={Source code editor by Microsoft.}}
\newglossaryentry{ws}{name=WebSocket,description={Communication protocol enabling full-duplex communication between client and server.}}
\newglossaryentry{ov}{name=Omega Verksted,description={Norwegian company specializing in industrial-grade 3D printers and CNC machines.}}
\newglossaryentry{pybind11}{name=\code{pybind11},description={C++/Python interoperability library.}}
\newglossaryentry{async-dash}{name=\code{async-dash},description={Plotly Dash extension with asynchronous capabilities using \code{asyncio}.}}
\newglossaryentry{dashextensions}{name=\code{dash-extensions},description={Plotly Dash extension library.}}
\newglossaryentry{pipeline}{name=pipeline,description={Sequence of interconnected components or stages.}}
\newglossaryentry{sensorpipeline}{name=Sensor Pipeline,description={The main pipeline collecting, managing and saving data.}}
\newglossaryentry{chrome}{name=Google Chrome,description={Web browser developed by Google.}}
\newglossaryentry{j1}{name=Snapmaker J1,description={IDEX 3D printer by Snapmaker.}}
\newglossaryentry{gcode}{name=G-code,description={A programming language for controlling CNC machines.}}
\newglossaryentry{fusion}{name=Fusion 360,description={A cloud-based CAD/CAM software by Autodesk.}}
\newglossaryentry{luban}{name=Luban,description={A software for controlling Snapmaker devices.}}
\newglossaryentry{apikey}{name=API key,description={A unique identifier used for authentication.}}
\newglossaryentry{qt}{name=Qt,description={A cross-platform C++ framework for GUI development.}}
\newglossaryentry{nicegui}{name=NiceGUI,description={A Python package for creating web-based GUIs.}}
\newglossaryentry{pico}{name=Raspberry Pi Pico,description={A microcontroller by Raspberry Pi Foundation.}}
\newglossaryentry{navbox}{name=Navbox,description={A navigation box, described in Chapter 4 of the Preproject.}}
\newglossaryentry{kartverket}{name=Kartverket,description={The Norwegian Mapping Authority.}}
\newglossaryentry{stim}{name=STIM300,description={A high-precision Inertial Measurement Unit (IMU) by Sensonor.}}
\newglossaryentry{qwiic}{name=Qwiic,description={A communication protocol by SparkFun.}}
\newglossaryentry{usb}{name=USB,description={Universal Serial Bus.}}
\newglossaryentry{symforce}{name=Symforce,description={A Python package developed by Skydio for symbolic computation and code generation based on Sympy.}}
\newglossaryentry{tinyusb}{name=TinyUSB,description={A USB device stack for embedded systems.}}
\newglossaryentry{container}{name=Container,description={A lightweight, isolated environment for running applications.}}
\newglossaryentry{docker}{name=Docker,description={A platform for creating and running containers.}}
\newglossaryentry{cmake}{name=CMake,description={A cross-platform build system.}}
\newglossaryentry{nvmmbuffer}{name=NvMmBuffer,description={A Hardware DMA buffer accessble from CPU, GPU and Multimedia ASICs on Jetson platforms.}}
\newglossaryentry{jetson}{name=Jetson,description={A family of embedded computing devices by NVIDIA.}}
\newglossaryentry{pubsub}{name=Publisher-subscriber,description={A messaging pattern where publishers distribute messages to subscribers without them directly knowing each other.}}
\newglossaryentry{gnss}{name=GNSS,description={Global Navigation Satellite System.}}
\newglossaryentry{yuv}{name=YUV,description={A color space with separate luminance and chrominance components.}}
\newglossaryentry{hsv}{name=HSV,description={A color space with separate hue, saturation and value components.}}
\newglossaryentry{alu}{name=ALU,description={Arithmetic Logic Unit.}}
\newglossaryentry{nsight}{name=Nsight,description={A suite of tools for profiling and debugging CUDA applications.}}
\newglossaryentry{asv}{name=ASV,description={Autonomous Surface Vehicle.}}

\newglossaryentry{numpy}{name=NumPy,description={A Python package for scientific computing.}}
\newglossaryentry{opencv}{name=OpenCV,description={A Python package for computer vision.}}
\newglossaryentry{av1}{name=AV1,description={A video compression standard with improved efficiency over H265.}}
\newglossaryentry{ip67}{name=IP67,description={Ingress Protection rating for dust and water resistance.}}
\newglossaryentry{p010}{name=\code{P010_10LE},description={A 10-bit YUV 4:2:0 format with interlaced U and V components.}}

\newglossaryentry{sympy}{name=SymPy,description={A Python library for symbolic mathematics.}}
\newglossaryentry{half2}{name=\code{__half2},description={A CUDA data type for two half-precision floating-point numbers.}}
\newglossaryentry{sm}{name=SM,description={Streaming Multiprocessor.}}
\newglossaryentry{chrontab}{name=\code{chrontab},description={A utility for scheduling tasks on Linux.}}

\newglossaryentry{numba}{name=Numba,description={A Python package for high-performance computing.}}

\newglossaryentry{pytorch}{name=PyTorch,description={A Python package for machine learning.}}

\newglossaryentry{cupy}{name=CuPy,description={A Python package to work with CUDA.}}
\newglossaryentry{cpp}{name=\code{C++},description={A programming language.}}
\newglossaryentry{eigen}{name=Eigen,description={A C++ template library for linear algebra.}}
\newglossaryentry{plotly}{name=Plotly,description={A Python package for data visualization.}}
\newglossaryentry{mantine}{name=Mantine,description={A React component library.}}
\newglossaryentry{markdown}{name=Markdown,description={A lightweight markup language.}}

\newglossaryentry{arena-api}{name=Arena API,description={The \gls{api} used to operate \lucid cameras.}}
\newglossaryentry{nsys}{name=Nsight Systems,description={A suite of tools for profiling and debugging CUDA applications.}}
\newglossaryentry{cuda}{name=CUDA,description={A parallel computing platform and programming model developed by NVIDIA.}}
\newglossaryentry{ffmpeg}{name=FFmpeg,description={A cross-platform multimedia framework.}}
\newglossaryentry{react}{name=React,description={A JavaScript library for building user interfaces.}}
% --------------------
% ----- Acronyms -----
% --------------------

\newacronym{adc}{ADC}{Analog to Digital Converter}
\newacronym{ai}{AI}{Artificial Intelligence}
\newacronym{api}{API}{Application Programming Interface}
\newacronym{asic}{ASIC}{Application Specific Integrated Circuit}
\newacronym{cad}{CAD}{Computer Aided Design}
\newacronym{cbm}{cmb}{Callback Manager}
\newacronym{cfa}{CFA}{Color Filter Array}
\newacronym{pfa}{PFA}{Polarization Filter Array}
\newacronym{cpfa}{CPFA}{Color and Polarization Filter Array}
\newacronym{cpu}{CPU}{Central Processing Unit}

\newacronym{dhcp}{DHCP}{Dynamic Host Configuration Protocol}
\newacronym{dla}{DLA}{Deep Learning Accelerator}
\newacronym{emmc}{eMMC}{Embedded Multi-Media Card}
\newacronym{fpga}{FPGA}{Field Programmable Gate Array}
\newacronym{gcd}{GCD}{Greatest Common Divisor}
\newacronym{gpio}{GPIO}{General Purpose Input Output}
\newacronym{gpu}{GPU}{Graphics Processing Unit}
\newacronym{gui}{GUI}{Graphical User Interface}
\newacronym{hls}{HLS}{HTTP Live Streaming}
\newacronym{hpc}{HPC}{High Performance Computing}
\newacronym{http}{HTTP}{Hypertext Transfer Protocol}
\newacronym{idp}{idp}{ID Provider}
\newacronym{imu}{IMU}{Inertial Measurement Unit}
\newacronym{isp}{ISP}{Image Signal Processor}
\newacronym{js}{JS}{JavaScript}
\newacronym{lla}{LLA}{Link-Local Addresses}
\newacronym{mhc}{MHC}{Malvar, He, and Cutler}
\newacronym{mtu}{MTU}{Maximum Transmission Unit}
\newacronym{npu}{NPU}{Neural Processing Unit}
\newacronym{ntpd}{NTPD}{Network Time Protocol Daemon}
\newacronym{nvenc}{NVENC}{NVIDIA Multi-Standard Video Encoder}
\newacronym{os}{OS}{Operating System}
\newacronym{phd}{PhD}{philosophiae doctor}
\newacronym{pps}{PPS}{Pulse Per Second}
\newacronym{ptp}{PTP}{Precision Time Protocol}
\newacronym{ram}{RAM}{Random Acces Memory}
\newacronym{regex}{RegEx}{Regular Expression}
\newacronym{rpf}{RPF}{Reverse Path Filtering}
\newacronym{rtos}{RTOS}{Real-Time Operating System}
\newacronym{rtsp}{RTSP}{Real Time Streaming Protocol}
\newacronym{sdk}{SDK}{Software Development Kit}
\newacronym{simt}{SIMT}{Single Instruction Multiple Threads}
\newacronym{skb}{SKB}{Socket Kernel Buffers}
\newacronym{spi}{SPI}{Serial Peripheral Interface}
\newacronym{ssd}{SSD}{Solid State Drive}
\newacronym{ssh}{SSH}{Secure Shell}
\newacronym{tcp}{TCP}{Transmission Control Protocol}
\newacronym{tov}{TOV}{Time of Validity}
\newacronym{udp}{UDP}{User Datagram Protocol}
\newacronym{utc}{UTC}{Coordinated Universal Time}
\newacronym{webrtc}{WebRTC}{Web Real-Time Communication}
\newacronym{wsl}{WSL}{Windows Subsystem for Linux}
\newacronym{i2c}{I2C}{Inter-Integrated Circuit}
\newacronym{lut}{LUT}{Look-Up Table}
\newacronym{fma}{FMA}{Fused Multiply-Add}
\newacronym{crc}{CRC}{Cyclic Redundancy Check}
\newacronym{simd}{SIMD}{Single Instruction Multiple Data}
\newacronym{cg}{CG}{Color Group}
\newacronym{pg}{PG}{Polarization Group}
\newacronym{cpg}{CPG}{Color and Polarization Group}
\newacronym{gil}{GIL}{Global Interpreter Lock}
\newacronym{dolp}{DoLP}{Degree of Linear Polarization}
\newacronym{aolp}{AoLP}{Angle of Linear Polarization}
\newacronym{io}{I/O}{Input/Output}
% \glsaddall

\glsunset{cpu}
\glsunset{gpu}
\glsunset{lla}

% --------------------
% ----- Shortcuts ----
% --------------------


\newcommand{\nvidia}{NVIDIA\xspace}
\newcommand{\jetson}{\gls{jetson}\xspace}
\newcommand{\sr}{Sensor Rig\xspace}
\newcommand{\jx}{Xavier\xspace}
\newcommand{\jo}{Orin\xspace}
\newcommand{\gs}{Gstreamer\xspace}
\newcommand{\cam}{Triton Polarizin Camera\xspace}
\newcommand{\cams}{Triton Polarizin Cameras\xspace}
\newcommand{\lucid}{Lucid Vision\xspace}
\newcommand{\preproject}{Pre-Project\xspace}
\newcommand{\master}{Master's\xspace}
\newcommand{\py}{Python\xspace}
\newcommand{\cpu}{\gls{gpu}\xspace}
\newcommand{\gpu}{\gls{cpu}\xspace}
\newcommand{\gui}{GUI\xspace}
\newcommand{\guif}{\gls{gui} framework\xspace}
\newcommand{\srgui}{\sr \gls{gui}\xspace}
